ABC - HTW Fits

### 2023-12-29 Model/abc_fit.qmd
big sync
abc plots

@@

  pgrid <- cbind(prior_samples,dist=abc_v_tetr$dist) |> mutate(dist=sqrt(dist))

>>>>

```{r}
library(cowplot)
file_names <- list.files(path = "Assets/tmp_plots", pattern = "density_plots.*\\.png$", full.names = TRUE)
# display the plots, with file_names as titles, use ggdraw
pacman::p_load(tidyverse, data.table, abc, future, furrr, here, patchwork, conflicted, cowplot)

# Load the file names
file_names <- list.files(path = "Assets/tmp_plots", pattern = "density_plots.*\\.png$", full.names = TRUE)

# Function to create a ggplot object from a PNG file
create_plot_from_png <- function(file_name) {
  png_image <- png::readPNG(file_name)
  ggplot() + 
    annotation_custom(rasterGrob(png_image), xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
    labs(title = basename(file_name)) +
    theme_void() + 
    theme(plot.title = element_text(hjust = 0.5, size = 10, face = "bold"))
}

# Create a list of ggplot objects
plot_list <- lapply(file_names, create_plot_from_png)

# Combine the plots using cowplot::plot_grid
combined_plot <- cowplot::plot_grid(plotlist = plot_list, ncol = length(plot_list))

# Display the combined plot
print(combined_plot)

@@

  pgrid <- cbind(prior_samples,dist=abc_result$dist) |> mutate(dist=sqrt(dist))
